\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{parskip}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor} % Provides more color options
\usepackage[bookmarks,colorlinks,linktoc=all,linkcolor=DarkGreen,urlcolor=Blue]{hyperref}
\usepackage{graphicx}
\usepackage[symbol]{footmisc}
\title{Team 2 Test Plan}
\author{Matt Kline, James Gordon, Tyler Kuske, and Creighton Long}
\begin{document}
\maketitle

\section*{Hardware Test Plan}

\begin{enumerate}
\item Test power rails and all signals to ensure that there are no shorts.
\item Test individual parts such as the laser diode and photodiodes using a breadboard.
\item Ensure the JTAG programmer for the CC430 works and that one can write software to the CC430.
\item Test the LEDs using simple CC430 software that turns them on and off in order to determine desired brightness
	and resistor values, ensuring that the current is low enough for the CC430 to sink.
\item Test that serial communications can be sent and received from the CC430 via the Cypress IC.
\item Ensure that the GPIO pins on the CC430 used for the radio are functioning using test points.
\item Attempt to send and receive data wirelessly between two CC430s.
\item Test the ZedBoard/FPGA link to the CC430 daughter card.
\item Test each gun component using its CC430:
	\begin{enumerate}
	\item Emit a beam using the laser diode
	\item Emit a sound using the Piezo buzer
	\item Test LEDs
	\item Ensure movement data is coming in through the accelerometer.
	\end{enumerate}
\item Test each target component using its CC430:
	\begin{enumerate}
	\item Ensure that the photodiodes are receiving laser signals.
	\item Test LEDs.
	\end{enumerate}
\end{enumerate}

\section*{Software Test Plan}

The software design will take advantage dependency injection to isolate the hardware into interfaces where possible.
This way mock hardware implementations can be used for testing and a large chunk of the software can be developed
independently of the backing hardware.
Portions of code that will remain relatively stable will have automated unit tests to help verify their correctness.
For some of the more rapidly-changing portions, unit tests may be omitted since the cost-to-benefit ratio
may not justify the time it takes to continuously adjust the tests.

Tested sections will include:
\begin{itemize}
\item All communication protocols, including:
	\begin{itemize}
	\item The JSON communication protocol between our ZedBoard and UI
	\item The serial protocol between the daughter board and the ZedBoard
	\item The serial protocol between the daughter board and targets
	\item The serial protocol between the daughter board and guns
	\end{itemize}
\item All transport layer code such as the TCP stream between the ZedBoard and UI and whatever error checking
	 (likely CRC-based) we implement for the radio comms.
\item The basic game state machines on the ZedBoard
\end{itemize}
\end{document}
